\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Consistency in confusion matrix notation, keywords. Closes #105. #203

Each subject (image cutout) is assigned a prior probability of
$2\times10^{-4}$ of containing a lens system. Every volunteer
is assigned an agent characterised by a $2\times2$ confusion matrix,
which quantifies the volunteer's ability to correctly classify an image
as containing a lens ($P_L$) or not containing a lens ($P_D$). The values of
these confusion matrix elements are determined based on the performance of the
volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
determined based on the fraction of simulated lenses (and, respectively, duds)
correctly classified. After every classification, the agent updates the
probability of the classified subject based on the volunteer's classification
and the confusion matrix, according to Bayes' theorem.
The agent's confusion matrix is updated after the
classification of every training image. The thresholds for the
probabilities {\bf to accept or reject a subject if it contains a lens or does
not contain one} can be chosen in SWAP. Those images which cross
these threshold values are ``retired'', and are not subsequently shown to the
volunteers. In this way, the crowd can use its time efficiently in
inspecting previously unclassified subjects.

>>>>

Each subject (image cutout) is assigned a prior probability of
$2\times10^{-4}$ of containing a lens system. Every volunteer
is assigned an agent characterised by a $2\times2$ confusion matrix~$\CM$,
which quantifies the volunteer's ability to correctly classify an image
as containing a lens ($\PL = P_L$) or not containing a lens ($\PD = P_D$).
The values of
these confusion matrix elements are determined based on the performance of the
volunteer on the training sample, specifically, $P_L$ (and $P_D$) is
determined based on the fraction of simulated lenses (and, respectively, duds)
correctly classified. After every classification, the agent updates the
probability of the classified subject based on the volunteer's classification
and the confusion matrix, according to Bayes' theorem.
The agent's confusion matrix is updated after the
classification of every training image. The thresholds for the
probabilities {\bf to accept or reject a subject if it contains a lens or does
not contain one} can be chosen in SWAP. Those images which cross
these threshold values are ``retired'', and are not subsequently shown to the
volunteers. In this way, the crowd can use its time efficiently in
inspecting previously unclassified subjects.
